---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# census_cde_demo

Data files are in data/<dataset_name>/distribution.<br />
Code for ingest and preparation of datasets is in src/01_data/<dataset_name>.<br />
Dataset documentation (if it exists) is in docs/01_data/<dataset_name>.<br />

## File List
A manifest with a list of the latest distribution files, along with md5 checksums, is available at /data/distribution_file_manifest.csv

Current files:<br />
```{r echo=FALSE}
library(jsonlite)
js <- read_json("data/distribution_file_manifest.json")

dt <- data.table::rbindlist(js)
```

```{r links-db, include = FALSE}
md_link <- function(text, link) {
  paste0("[", text, "](", link, ")<br />", collapse = "")
}
```

`r md_link(dt$file, dt$file_path)`

## New Dataset Creation

1. Create new yaml settings file and place in /src/01_data/00_dataset_yaml_files. For example:
<pre><code>
  ---
  dataset_info:
    dataset_type: "data"             
    data_agency_company_abbrv: "dhs"
    data_center_program: "hifld"
    dataset_general_subject: "Nursing Homes"
    dataset_sub_subject: ""
    dataset_region_type: ""
    dataset_geo_coverage: "us"
    dataset_geo_level: "pl"         
    dataset_start_year: "2022"
    dataset_end_year: ""
    dataset_source_files:
      - type: "data"    
        format: "geojson"
        url: "https://opendata.arcgis.com/datasets/78c58035fb3942ba82af991bb4476f13_0.geojson"
      - type: "doc"
        format: "xml"
        url: "https://www.arcgis.com/sharing/rest/content/items/78c58035fb3942ba82af991bb4476f13/info/metadata/metadata.xml"
</code></pre>

2. Open /src/01_data/01_set_up_new_datasets.R and add new new_dataset_setup command, and run. This creates a filename all of the folders that will go along with this dataset. For example:
<pre><code>
  # US DHS HIFLD Nursing Homes 2022
  new_dataset_setup(dataset_info_yml_file_path = "src/01_data/00_dataset_yaml_files/us_hifld_nursing_homes_2022.yml",
                    code_files = "R",
                    overwrite = TRUE)
</code></pre>

3. Now go to the folder created for this dataset in /src/01_data/<name of new dataset> and open the first ingest file (01_ingest_file_1.R). There should now be one file for ingest for each source file you listed in the yaml file.

Running the already created code should download the source file and place it in the /data/<name of new dataset>/original folder.

4. Now open the prepared dataset preparation file, 02_prepare.R. 
This file has the basic steps and some of the needed code already prepopolated.

Once finished, you will have a final dataset in /data/<name of new dataset>/distribution.
